\section{Other concrete examples of issues showed in the JFSA's report}
\label{appendix_report_examples}

The following is the other examples of issues showed in the JFSA's interim report from investigation and monitoring that are not discussed in section 2.

\begin{enumerate}
  \item First line: Issues around advertisements
   \begin{itemize}
     \item An exchange does not have the internal review process of the contents of the advertisement.
     \item An exchange used TV advertisement on which famous celebrity calls the name of the certain cryptocurrency to encourage customers to buy it while explains risks only in few seconds.
     \item An advertisement shows a particular discount period and investment profitability that customers cannot verify.
   \end{itemize}

  \item Second line: Issues around AML/CFT
  \begin{itemize}
    \item Many exchanges fail to confirm customers' characteristics and purpose of the transaction as well as conduct pre-examination to exclude transactions with the organized crime group.
    \item There are cases of lack of appropriate guidelines regarding checking process of impersonation
    \item An exchange lacks monitoring process and system to detect suspicious activities.
  \end{itemize}

  \item Second line: Issues around segregation of customers' assets
  \begin{itemize}
    \item Several exchanges fail to reconcile between bank account balance for customers' assets and account balance on their own server.
    \item An exchange fails to find out the cause of the frequent incident that the customers' bank account balance becomes below the balance on their own server.
    \item Several exchanges create general ledger only and fail to keep books on daily transactions, the ledger of their own account, and the ledger of customers' account, all of which are required by regulation.
  \end{itemize}

  \item Second line: Issues around system safety management
  \begin{itemize}
    \item Several exchanges neither keep records of system troubles that keep date/time and the number of incidents, impact, countermeasures, and changes to prevent re-emergence nor understand the root cause of the system troubles even though they had many troubles.
    \item In the system development phase, an exchange neither establishes documents for requirement definition, development plan, and architecture specification nor conducts implementation tests at the frontline.
  \end{itemize}

  \item Second line: Issues around customer protection
  \begin{itemize}
    \item When an exchange issues its own currency, it fails to explain the financial situation and business model of the issuing exchange to customers.
    \item Another exchange issuing new currency fails to disclose important information that management of the exchange gain a huge bonus for sale of the cryptocurrency.
    \item Several exchanges fail to conduct a training program on customers' information management and allow anyone in the company and third-party contractor to access to it or even bring out from the company.
    \item Several exchanges fail to either keep records of the customer complains or improve the business practice based on the complaints. They just ignore them or randomly address them case by case basis.
  \end{itemize}

  \item Third line: Issues around internal audit
  \begin{itemize}
    \item Many exchanges fail to establish a plan for internal audit.
    \item Even when an internal audit was conducted, several exchanges fail to do it based on the risk assessment.
    \item Several also fail to conduct the audit on the third party contractor.
  \end{itemize}

  \item Corporate culture and governance
  \begin{itemize}
    \item Within many exchanges, board meeting fails to discuss how to mitigate risks associated with their business as financial institutions.
    \item Many exchanges fail to disclose their business and financial situation to customers in an easy-to-understand manner, which other financial institutions are required.
  \end{itemize}

\end{enumerate}
