\section{Details of system model}
\label{appendix_system_model}
\begin{itemize}
 \item Customer Interface\\
       Provides screen and input functions such as login process, account management (deposit/withdrawal instruction etc.) and trade instruction for the customers(users). Web application, API, etc.
 \item Customer Authentication Function\\
       Performs user authentication process for login to the cryptocurrency exchange.
 \item Customer Credential Database\\
       Manages required IDs for login and verification information related to user authentication process (f.g password verification info.).
 \item Customer Assets Management Function\\
       A group of functions to manage customer accounts. Receive instructions for deposit or withdrawal (outgoing coins) and perform processing according to the user instructions. Refer or update asset data.
 \item Blockchain Node\\
       Connects to another blockchain nodes to retrieve blockchain data.
 \item Incoming transaction management Function\\
       Checks transaction stored in blockchain and confirm whether incoming coins are involved in the specified addresses.
 \item Order processing function\\
       A group of functions that receives sales instructions from customers and performs processing related to trading of crypto assets. Refers and updates asset data based on asset data.
 \item Assets Database\\
       Manages holdings of fiat currencies and crypto assets. It does not include the private keys for signing transactions. Managed separately from the assets of the excahnge for each customer.
 \item Transaction Singing Function, which includes Transaction Generator, Transaction Broadcaster, Transaction Signing Function, Address Management,
       \begin{itemize}
        \item Transaction Generator\\
              Generates transactions to be sent to the blockchain based on instructions from the customer asset management system or the exchange management system, and Private Signature Key Management Function
        \item Transaction Broadcaster\\
              Sends the signed transaction to the blockchain. Connects to nodes of the another nodes on the blockchain.
        \item Transaction Signing Function\\
              Generates digital signatures based on the instructed transaction contents and the private signature key (with IDs and addresses).
        \item Address Management\\
              Manages public keys with related to the private signature keys, or addresses (such as values calculated from the public keys).
        \item Private Signature Key Management Function\\
              Manages the signing keys of the crypto assets (the keys used for the transaction signing). Sometimes it is separated into the cold-wallet as security countermeasure. “Signature key generator” creates signature keys. The generated keys are registered in the signature key management unit, and the public keys and addresses are registered in the address management units.
       \end{itemize}
 \item Exchange Operation Modules\\
       A group of functions for exchanges’ administrators. Based on operations from administrators, instructs generation of generating new signature keys or transfer crypto assets.
 \item Operator Authentication Function\\
       Authenticates the administrator users.
 \item Operator Audit Database\\
       Manages verification data related to the authentication processes of the administrators.
\end{itemize}
